---
title: "Untitled"
author: "Jo Saul"
date: "2022-11-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faux)
library(tidyverse)
library(lavaan)
```

### Instructions

1. Edit this code so that it simulates 200 observations, with the self esteem variables all correlated at 0.4
```{r}
sim1 <- rnorm_multi(n=200,
              mu=0,
              sd=1,
              r=0.4,
              empirical=T,
              varnames=c('selfesteem1', 'selfesteem2', 'selfesteem3', 'selfesteem4'))
```

2. Edit this code so that it models a 1 factor latent variable 'selfesteem' comprising the 4 items of sim1
```{r}
model <- ' 
sim1<-selfesteem1+ selfesteem2 + selfesteem3 + selfesteem4
'
mod <- cfa(model, sim1)
summary(mod)

```


Add a chunk here and put in some constructive feedback about the course.

#Everything in the course has been very good! I am grateful for excellent communications and responses to hot questions. I would just say that it might be helpful for future students to have the answer to the pre-practical before the practical so they can check their mistakes. It would also be good to have 1-1 statistics support towards the end of the week as well as Mondays or Tuesdays.
